\documentclass[a4paper,12pt]{article}

\title{gwybodaeth Documentation}
\author{Iestyn Pryce}

\include{vc}

\begin{document}
\maketitle

\begin{center}
Revision: \VCRevision
\end{center}

\section{Usage}

\textbf{gwybodaeth} is a set of Perl classes for convesion of data into RDF. It can be either used from a command line tool or via a CGI web
script. 

\subsection{Command Line}
The current command line tool takes two arguments, the first being a URL
or path to the data file, the second being a URL or path to the mapping file:

\begin{verbatim}
./gwyboadaeth data1.csv dataMap1.N3
\end{verbatim}
\begin{verbatim}
./gwyboadaeth http://foo.bar.com/data1.csv http://foo.bar.com/dataMap1.N3
\end{verbatim}

\subsection{CGI}
In the URL \verb!src! is used to assign the data source and \verb!map! is used
to assign the map source. The CGI script currently only works with data and maps
which are online.

{ \tiny  \begin{verbatim}
http://127.0.0.1/~imp25/cgi-bin/gwybodaeth.cgi?src=http://rdf123.umbc.edu/csv/office1.csv&map=http://rdf123.umbc.edu/map/officeMap1.N3
\end{verbatim} } 

With the use of the CGI script it is important to remember to escape characters
such as \& in the URLs to data/maps or the script will treat them as delimiters.

\section{Functionality}
\subsection{Input}
The input format currently supported is CSV. The use of `start row,
\emph{num}' is supported if you wish to start slurping the data from a row other
than the first row.

\subsection{Maps}
The mapping files should be based on
N3\footnote{http://www.w3.org/DesignIssues/Notation3.html}. An example of the
currently supported grammer is shown in Figure ~\ref{fig:map4}. This mapping
makes each row a Person subject with the email taken from the third
column; the name being a concationation of the first and second columns; the
nickname being taken from the first column; office number and phone being taken
from the the fifth and fourth columns respectively. The object for the
workAddress predicate is taken from the \verb!<Ex:$5>! function which defines a
work:Office subject.
\begin{figure}[!h]
{ \small \begin{verbatim}
@prefix work:    <http://www.foo.org/work/> .
@prefix foaf:    <http://xmlns.com/foaf/0.1/> .
@prefix rdf:     <http://www.w3.org/1999/02/22-rdf-syntax-ns#> .
@prefix :        <#> .

<Ex:$5>
      a       work:Office ;
      work:number "Ex:$5" ;
      foaf:phone "Ex:$4" .

[]    a       foaf:Person ;
      foaf:mbox "Ex:$3" ;
      foaf:name "Ex:$1+' '+$2" ;
      foaf:nick "Ex:$1" ;
      foaf:officeNumber "Ex:$5" ;
      foaf:officePhone "Ex:$4" ;
      foaf:workAddress <Ex:$5> .
\end{verbatim} }
\caption{RDF123's officeMap3.N3}
\label{fig:map4}
\end{figure}

\begin{figure}[!h]
{ \small \begin{verbatim}
@prefix rdf:     <http://www.w3.org/1999/02/22-rdf-syntax-ns#> .
@prefix foaf:    <http://xmlns.com/foaf/0.1/> .
@prefix :        <#> .

[]    a       foaf:Person ;
      foaf:mbox "Ex:$2" ;
      foaf:name "Ex:$1" ;
      foaf:officeNumber "Ex:$3" ;
      foaf:supervisor
              [ a       foaf:Person ;
                foaf:name "Ex:$4"
              ] 
\end{verbatim} }
\caption{RDF123's officeMap2.N3}
\label{fig:map2}
\end{figure}

The map example shown in Figure ~\ref{fig:map2} shows the use of the [ ] syntax
to allow inline functions. This is useful for short functions, however for more
advanced functions the grammer used in Figure ~\ref{fig:map4} is more suitable.

An explination of a number of the specific mapping grammer is in Table
~\ref{tab:grammer}.  

\begin{table}
\begin{tabular}[!h]{|c|p{12cm}|}
\hline
\verb!"Ex:${num}"!&The value of the column \emph{num} is placed here as the
object.\\
\hline
\verb!<Ex:${num}>!&This is a function. On its own line it defines the following block as the contents of the function. As an object it calls the defined
function.\\ 
\hline
+ & Allows for the concatination within the object.\\ 
\hline
[ a ... ] . & Define an inline function. \\
\hline
\end{tabular}
\caption{Table of supported N3 grammer.}
\label{tab:grammer}
\end{table}
\end{document}
